% Validation section

The validation experiments in this section use \textbf{shortest path (metric) distances}. Results for angular (simplest path) distances show qualitatively similar patterns, with the key quantitative differences captured by the separate model parameters in Table~\ref{tab:model_parameters}.

\subsection{Synthetic Networks}

We compare three approaches on the synthetic network topologies: full computation without sampling (baseline), uniform sampling with a single probability across all distances, and adaptive per-distance calibrated sampling. For fair comparison, uniform sampling uses the reach-weighted mean probability from the adaptive plan, giving both approaches equivalent computational budget.

Uniform sampling reduces computation but with inconsistent accuracy: $\rhosp$ varies widely depending on topology and distance, with short distances falling well below target accuracy while long distances exceed it. Adaptive sampling maintains $\rhosp \geq 0.95$ across all topologies, with speedup increasing at longer distances. Betweenness shows higher variance than harmonic closeness, confirming the need for separate models.

The critical advantage of adaptive sampling is consistent accuracy \emph{across all distances}. With uniform sampling, short distances show poor accuracy due to low effective sample size, while long distances are over-sampled (Figure~\ref{fig:headline}). Adaptive sampling maintains $\rhosp \geq 0.95$ at all distances by using full computation at short distances and aggressive sampling at long distances.

\subsection{Real-World Networks}
\label{sec:spatial_analysis}

We validate the empirical models on street networks from London, Madrid, and Phoenix, downloaded from OpenStreetMap using \cityseer{}. These networks vary substantially in topology and density, providing a rigorous test of model generalisability.

The empirical models generalise well to real-world networks. Predicted $\rhosp$ values are within $\pm 0.05$ of observed values in most cases, and the conservative (10th percentile) model provides reliable lower bounds with no systematic bias toward over- or under-prediction. Adaptive sampling maintains target accuracy on real-world networks, with speedup characteristics consistent with synthetic results: as distance increases, so too does the speedup.

We also investigated spatial heterogeneity in estimation accuracy across network areas. Harmonic closeness shows a non-monotonic U-shaped pattern where transitional zones (Q2--Q3 reachability) have lower accuracy than boundary or core areas. Betweenness accuracy increases monotonically with reachability as expected. Full spatial analysis including Moran's I statistics is provided in Appendix~C.
