% =============================================================================
% Appendix A: Technical Details
% =============================================================================

\subsection{Synthetic Network Generation}

Synthetic networks are generated using tile-based templates. Each template defines a connectivity pattern within a single tile; tiles are then arrayed to create networks of the desired extent.

\begin{description}
\item[Trellis] A regular grid with diagonal connections, representing highly connected urban cores. Average degree $\approx 4$.

\item[Tree] A hierarchical branching structure where each node connects to at most 3 others. Represents suburban cul-de-sac development. Average degree $\approx 2.3$.

\item[Linear] A constrained grid with fewer cross-connections than trellis. Intermediate connectivity. Average degree $\approx 3$.
\end{description}

Networks are tiled 24$\times$24 to achieve approximately 12km extent, then the largest connected component is extracted. Node positions are perturbed slightly to avoid perfectly regular spacing.

\subsection{Live Node Buffer Implementation}

Edge artifacts arise when nodes near network boundaries have truncated catchments. We eliminate these by computing an inward buffer from the convex hull of all nodes.

Algorithm:
\begin{enumerate}
\item Compute the convex hull of all node positions
\item Apply a negative (inward) buffer equal to the maximum analysis distance
\item Mark nodes inside the buffered polygon as ``live''
\item Compute accuracy metrics using only live nodes
\end{enumerate}

For synthetic networks, the buffer is \syntheticBuffer{}km (matching the maximum 4km analysis distance). For GLA validation, the buffer is \glaBuffer{}km (matching the maximum 20km analysis distance).

\subsection{Centrality Implementation}

Centrality measures are computed using the \cityseer{} library, which implements distance-weighted local centrality with efficient shortest-path algorithms.

\textbf{Harmonic closeness}:
\begin{equation}
C_H(v; d_{\max}) = \sum_{u: d(v,u) \leq d_{\max}} \frac{1}{d(v, u)}
\end{equation}

\textbf{Betweenness}:
\begin{equation}
C_B(v; d_{\max}) = \sum_{\substack{s, t: s \neq v \neq t \\ d(s,t) \leq d_{\max}}} \frac{\sigma_{st}(v)}{\sigma_{st}}
\end{equation}

Both measures are computed using Dijkstra's algorithm with early termination at $d_{\max}$.

\subsection{Sampling Implementation}

Source nodes are sampled using uniform random selection with a specified probability $p$. For reproducibility, random seeds are fixed for each configuration.

Sampled centrality is computed by:
\begin{enumerate}
\item Selecting a random subset $S$ of source nodes with probability $p$
\item Computing centrality contributions from sources in $S$ only
\item Scaling results by $1/p$ to produce unbiased estimates
\end{enumerate}

The scaling is exact for betweenness (each source contributes independently to path counts). For harmonic closeness, the scaling is approximate but accurate for our parameter range.

\subsection{Model Fitting Procedure}

\subsubsection{Fitting $k$}

For each (topology, distance) configuration:
\begin{enumerate}
\item Sort by sampling probability
\item Find minimum $p^*$ where $\rho \geq \targetRho$
\item Compute $k_{\text{implied}} = p^* \cdot \sqrt{r}$
\end{enumerate}

The final $k$ is the maximum $k_{\text{implied}}$ across all \nConfigs{} configurations, plus a 10\% safety margin: $k = 1.1 \times \max(k_{\text{implied}}) = \kProp$.

\subsubsection{Fitting $\minEffN$}

Effective sample sizes are binned: $[0, 50), [50, 100), \ldots, [750, 1000)$.

For each bin, we compute the \emph{local} success rate: the fraction of observations in that bin achieving $\rho \geq \targetRho$.

The floor $\minEffN$ is the lower bound of the first bin achieving $\geq 95\%$ local success rate. This avoids the issue where cumulative success rates are inflated by high-$\effn$ observations.

The fitted value is $\minEffN = \minEffN$, corresponding to the $[350, 400)$ bin which achieves \floorSuccessRate{}\% success rate.

\subsection{GLA Network Preprocessing}

The Greater London Authority road network is sourced from Ordnance Survey Open Roads data (GeoPackage format).

Preprocessing steps:
\begin{enumerate}
\item Remove invalid and empty geometries
\item Explode multi-part geometries
\item Build NetworkX graph from edges
\item Remove filler nodes (degree-2 nodes that don't represent junctions)
\item Remove dangling nodes (dead-end segments $< 20$m)
\item Consolidate nearby nodes (threshold 1m)
\item Extract largest connected component
\end{enumerate}

Final network: $\approx$ \glaNnodes{} nodes.

\subsection{Reproducibility}

All analysis scripts and data are available at:
\begin{center}
\texttt{https://github.com/benchmark-urbanism/cityseer-api/tree/master/analysis/sampling}
\end{center}

Key files (in \texttt{scripts/} subdirectory):
\begin{itemize}
\item \texttt{00\_generate\_cache.py}: Regenerate cached data
\item \texttt{01\_fit\_model.py}: Fit proportional constant $k$
\item \texttt{02\_fit\_floor.py}: Fit minimum floor $\minEffN$
\item \texttt{03\_combined\_model.py}: Combine model parameters
\item \texttt{04\_validate\_gla.py}: Validate on GLA network
\item \texttt{05\_practical\_guide.py}: Generate practical guidance
\item \texttt{06\_sync\_config.py}: Sync parameters to library
\item \texttt{07\_generate\_macros.py}: Generate LaTeX macros from JSON
\end{itemize}

Model parameters are stored in \texttt{output/sampling\_model.json} and synced to \texttt{pysrc/cityseer/config.py} for library integration. LaTeX macros are auto-generated by \texttt{07\_generate\_macros.py} into \texttt{paper/tables/model\_macros.tex}.
